\input{Pre.tex} %----- put in Preamble


\title{Seminar paper \\ Nonlocal games and the Grothendieck-Tsirelson inequality}
\author{Maxi Brandstetter, Arne Heimendahl, Felix Kirschner}

\begin{document}
\pagenumbering{roman}	

%adjust equation numberung 
\numberwithin{equation}{section}


\begin{abstract}
This paper is an elaboration and review of nonlocal games and the Grothendieck-Tsirelson inequality, our topic for the seminar \emph{Introduction to quantum information theory and quantum computing}, which took place on the 20th and 21st of September 2018 at the University of Cologne. We introduce some of the mathematical groundwork that helps us describe the quantum mechanical world. We define nonlocal games, which are mathematical concepts that enable us to explore the difference of classical and quantum mechanics. An example is given, that highlights the phenomenon of entanglement, which gives correlated measurement outcomes, where these are not expected. The mathematical structures underlying nonlocal games are discussed in detail and again it is shown that the quantum mechanical world provides more powerful tools than the of classical mechanics. Last but not least, we come across one of the many instances where the celebrated Grothendieck inequality comes in handy. The beautiful proof of the Grothendieck inequality by Krivine is given and the Grothendieck-Tsirelson theorem is elaborated. 
\end{abstract}


\maketitle	
\tableofcontents
	
	
\newpage	
\pagenumbering{arabic}



%\section{Einleitung}    %%Einleitung erstmal raus 
	\vspace{8pt}
%	\input{chapters/Einleitung.tex}


%---------------------------------------------------------------------------
\let \oldsection \section
\renewcommand{\section}{\vspace{15pt plus 8pt}\oldsection}
\let \oldsubsection \subsection
\renewcommand{\subsection}{\vspace{10pt plus 3pt}\oldsubsection}
%---------------------------------------------------------------------------



\newpage
\section{Introduction} 
	\vspace{8pt}
	\input{chapters/FelixTeil.tex}


\section{Local and Quantum correlation matrices} 
	\vspace{8pt}

	\input{chapters/ArnesTeil.tex}
\section{Grothendieck-Tsirelson Theorem} 
	\input{chapters/MaxisTeil.tex}
 
 
\appendix

	\input{chapters/Appendix.tex}	


%\bibliography{literature}						  % Literature
%\bibliographystyle{plain}
\newpage 
\begin{thebibliography}{99999}
	
	% Das Literaturverzeichnis wird mit diesem Befehl in das Inhaltsverzeichnis eingebunden
	%\addcontentsline{toc}{section}{Bibliography}
	
	\bibitem[Au]{Au} G. Aubrun; S. J. Szarek. {\em Alice and Bob Meet Banach: The Interface of Asympototic Geometry Analysis and Quantum Information Theory.} Graduate Studies in Mathematics, American Mathematical Society, 2017.
	\bibitem[Br]{Br}J. Bri\"{e}t. {\em Grothendieck Inequalities, Nonlocal Games and Optimization.} Institute for Logic, Language and Computation, Amsterdam, 2011.
	\bibitem[KNP]{KNP} F. Kirschner; Simon Nietz; Fabian Portner. {\em Seminar Paper Quantum Chromatic Number of a Graph.} University of Cologne, 2017.
	\bibitem[MR]{MR} L. Man$\check{c}$inska; D. E. Roberson. {\em Note on the Correspondence Between Quantum Correlations and the Completely Positive Semidefinite Cone}. Unpublished manuscript, 2014.
	
	
	
\end{thebibliography}
	
\end{document}